---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# taitratools

<!-- badges: start -->
<!-- badges: end -->

Taitra Tools package gather all useful helper functions.

Most function in `taitratools` are prefix with `tt_`.

You can list all source path with `tt_ls()` funciton, read data with `tt_read_table()` or `tt_read_mof()` ...


``` r
# install.packages("devtools")
devtools::install_github("chinhungtseng/taitratools")
```
## Example

### List all source path

```{r}
library(taitratools)

tt_ls()
```

Get source path with `tt_get_path(PATH NAME)`
Read file with `tt_read_table`

```{r}
path <- tt_get_path("PATH_AREA")
path

area_tbl <- tt_read_table(path)
head(area_tbl)
```

### MOF 

This is a basic example which shows you how to read data from MOF:

```{r}
# Default is `export` and `usd`
sample1 <- tt_read_mof("2019-01", "2019-02")
head(sample1)
```

If you want to read data with past year, you can set `period = N`,

```{r}
# Read this year and last year, set period = 1
sample2 <- tt_read_mof("2019-01", "2019-02", period = 1)
head(sample2)
```

Read mof data and input specified industry

```{r}
ind_sample1 <- rpt_mof_industry_region("2019-01", "2019-03", "手工具", "country")
# The output is a list.
head(ind_sample1[[1]])

ind_sample2 <- rpt_mof_industry_region("2019-01", "2019-03", "手工具", "area")
head(ind_sample2[[2]])
```

### Other functions

```{r}
# Create a sample data
sample3 <- tt_read_mof("2019-01", "2019-03", period = 1)

# output by year
output3_1 <- rpt_country_value(sample3, by = "year")

head(output3_1)

# output by month
output3_2 <- rpt_country_value(sample3, by = "month")

head(output3_2)
```

```{r}
# Create a sample data
sample4 <- tt_read_mof("2019-01", "2019-03", period = 1)

# output by year
head(rpt_area_value(sample4, by = "year"))

# output by month
head(rpt_area_value(sample4, by = "month"))
```














